---
title: "Gapminder Shiny App"
author: "Author: Andrés Nazarian"
date: "2020-09-20"
output: 
  ioslides_presentation: 
    keep_md: yes
---
## Objective

The objective of this app is to let the user gain easy to use insights of the data contained on the Gapminder dataset.

Data has been obtained from the 'gapminder' library on CRAN. The dataset is an excerpt of the Gapminder data on life expectancy, GDP per capita, and population by country every 5 years.

```{r}
library(gapminder)
head(gapminder,4)
```


## App description

The app is simple and easy to use. It has 4 tab panels with different analysis for the user to query:

- Interaction over time
- Geospacial analysis
- Trends
- Linear predictions

## Look at the past

The first three tabs allow us to look at past trends to understand the data. For example, if we look at historical life expectancy in Africa, the user can distinguish certain historical events, such as the Genocide in Rwanda in the '90.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(plotly,tidyverse)

ggplotly(ggplot(filter(gapminder,continent=="Africa"), 
       aes(x=year,y=lifeExp,color=country))+geom_line()+
       theme_bw()+theme(legend.position="none")+
       scale_color_manual(values=gapminder::country_colors))
```

## Infere to the future

The final tab allows the user to define a linear model by country and predict the values for a given year (until 2100).

IMPORTANT: Take into account that this are simple linear regressions for the activity purpose. Thus, the user must consider the characteristics of the model when interpreting the results. Otherwise some predictions may result illogical, specially when considering the life expectancy variable.


THANKS FOR WATCHING ;)

